---
title: "03-lab3"
format: html
---

## Q1
```{r, message=FALSE}
library(stringr)
log <- readLines("outputs/flye_output/flye.log")
start <- grep("Assembly statistics:", log)
stats <- log[(start+2):(start+7)]
stats <- str_replace_all(stats, "\t", "")
stats <- strsplit(stats, ":")
stats_df <- as.data.frame(do.call(rbind, stats))
print(stats_df)
```

Since the total length is only 10Mb long, and the expected is 12Mb, it does not seem to be the complete genome. The mean coverage is only 6 which is very low 


## Q2
The BUSCO scores were: C:42.8%[S:42.7%,D:0.1%],F:0.7%,M:56.6%,n:3282,E:6.6%
These scores are not great, given that over half of the expected marker genes are missing from the assembly. 

The BUSCO N50 was 26 kbp, and the flye N50 was 28,944, so 2000 bp higher than BUSCO

The total length from BUSCO was 10,048,474, which is overall shorter than the flye result of 10,217,386

## Q3
The genome fraction from quast was 4.773%, which is significantly lower than the 42.8% completeness given by BUSCO

The duplication ratio was 1.019

There were 2 misassemblies with a length of 102,154 bp. ??????

## Q4
```{r}
full <- readLines("data/S288C_UCSC.fna")
headers <- grep(">", full)
chunk <- full[headers[1]:(headers[2]-1)]
writeLines(chunk, "outputs/R64_chr1.fna")
```

## Q5
```{r, message=FALSE}
library("IRanges")
library("GenomicRanges")
library("Rsamtools")
library("GenomicAlignments")
library("Gviz")
```

```{r}
bam_file <- "outputs/alignment.sorted.bam"
bam <- BamFile(bam_file)
alns <- readGAlignments(bam)
gr_alns <- granges(alns)
range(gr_alns)
```

```{r}
ranges(gr_alns)
```

```{r}
aln_track <- AnnotationTrack(gr_alns, name = "Contigs", genome = "sacCer3", chromosome = "chrI")
axis_track <- GenomeAxisTrack()
plotTracks(list(axis_track, aln_track),
           from = min(start(gr_alns)),
           to = max(end(gr_alns)),
           main = "Contig Alignments to Chromosome 1")
```

There are only 9 contigs aligning to chromosome 1

Adding up the widths of all the contigs gives us 16,476 bp. Dividing this by the total length of chromosome 1 (230 kbp) gives us 0.07% coverage. This aligns with our quast results, which showed that there was only about 4% alignment coverage in the whole genome.

## Q6
```{r, eval=FALSE}
library(Biostrings)
consensus <- readDNAStringSet("outputs/medaka_round2/consensus.fasta")
longest_index <- which.max(consensus) 
longest <- consensus[longest_index]
writeXStringSet(longest, filepath = "outputs/longest_contig.fasta")
```

## Q7 
```{bash, eval=FALSE}
samtools view -bS outputs/cds_aln.sam > outputs/cds_aln.bam
samtools sort outputs/cds_aln.bam -o outputs/cds_aln.sorted.bam
samtools index outputs/cds_aln.sorted.bam
```
